\pkg{systemfit}: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-12-27 paper/trunk/systemfit_estimation.tex
replaced single quotes (') around "fitted" by (automatically) directed double quotes (°) (2 times)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@915 591db2bd-e0a0-4d22-8c19-2192dbb7da31

At the first stage new ('fitted') regressors are obtained by
\begin{equation}
   \XHat_i = Z_i \left( Z_i^\top Z_i \right)^{-1} Z_i^\top X_i .
\end{equation}
Then, these 'fitted' regressors are substituted for the original regressors
in Equation~\ref{eq:ols-wls-sur}
to obtain unbiased 2SLS, W2SLS, or 3SLS estimates of $\beta$ by
\begin{equation}
   \bHat
   = \left( \XHat^\top \OHat^{-1} \XHat \right)^{-1} \XHat^\top \OHat^{-1} y ,
   \label{eq:2sls-w2sls-3sls}
\end{equation}
where
\begin{equation}
   \XHat =
   \left[ \begin{array}{cccc}
      \XHat_1 & 0       & \cdots & 0\\
      0       & \XHat_2 & \cdots & 0\\
      \vdots  & \vdots  & \ddots & \vdots\\
      0       & 0       & \cdots & \XHat_G
   \end{array}\right] .
\end{equation}
An estimator of the covariance matrix of the estimated coefficients
can be obtained from Equation~\ref{eq:cov-ols-wls-sur} analogously.
Hence, we get
\begin{equation}
   \COVHat \left[ \bHat \right]
   = \left( \XHat^\top \OHat^{-1} \XHat \right)^{-1} .
   \label{eq:cov-2sls-w2sls-3sls}
\end{equation}

>>>>

At the first stage new (°fitted°) regressors are obtained by
\begin{equation}
   \XHat_i = Z_i \left( Z_i^\top Z_i \right)^{-1} Z_i^\top X_i .
\end{equation}
Then, these °fitted° regressors are substituted for the original regressors
in Equation~\ref{eq:ols-wls-sur}
to obtain unbiased 2SLS, W2SLS, or 3SLS estimates of $\beta$ by
\begin{equation}
   \bHat
   = \left( \XHat^\top \OHat^{-1} \XHat \right)^{-1} \XHat^\top \OHat^{-1} y ,
   \label{eq:2sls-w2sls-3sls}
\end{equation}
where
\begin{equation}
   \XHat =
   \left[ \begin{array}{cccc}
      \XHat_1 & 0       & \cdots & 0\\
      0       & \XHat_2 & \cdots & 0\\
      \vdots  & \vdots  & \ddots & \vdots\\
      0       & 0       & \cdots & \XHat_G
   \end{array}\right] .
\end{equation}
An estimator of the covariance matrix of the estimated coefficients
can be obtained from Equation~\ref{eq:cov-ols-wls-sur} analogously.
Hence, we get
\begin{equation}
   \COVHat \left[ \bHat \right]
   = \left( \XHat^\top \OHat^{-1} \XHat \right)^{-1} .
   \label{eq:cov-2sls-w2sls-3sls}
\end{equation}
